### 2014-11-01 contract-language.tex
edits

\item \textbf{Causal consistency}: Causally consistent operations are
  required to see a causally consistent snapshot of the object state,
  including the actions performed on the same session.  The latter
  requirement entails that if two operations $o_1$ and $o_2$ from the same
  session are applied to two different replicas $r_1$ and $r_2$, the second
  operation cannot be discharged until the effect of $o_1$ is merged with
  $o_2$ in both $r_1$ and $r_2$. The \cf{getBalance} operation requires
  causal consistency, as it requires the operations from the same session to
  be visible, which cannot be guaranteed under just eventual consistency. We
  assume that causality is only tracked through operations on the same
  object; two operations in the same session but on different objects are
  considered causally unrelated under this definition. Stores typically
  avoid tracking causality across objects to mitigate overheads when
  causality tracking is unnecessary. The corresponding store semantics is
  captured by the contract $\ccc$ defined below:

@@

>>>>

\item \textbf{Causal consistency}: Causally consistent operations are required
	to see a causally consistent snapshot of the object state, including the
	actions performed on the same session.  The latter requirement entails that
	if two operations $o_1$ and $o_2$ from the same session are applied to two
	different replicas $r_1$ and $r_2$, the second operation cannot be discharged
	until the effect of $o_1$ is merged with $o_2$ in both $r_1$ and $r_2$. The
	\cf{getBalance} operation requires causal consistency, as it requires the
	operations from the same session to be visible, which cannot be guaranteed
	under just eventual consistency. We assume that causality is only tracked
	through operations on the same object. The corresponding store semantics is
	captured by the contract $\ccc$ defined below:

@@

  %%; two operations in the same session but on different objects are
  %% considered causally unrelated under this definition. Stores typically
  %%avoid tracking causality across objects to mitigate overheads when
  %% causality tracking is unnecessary.

### 2014-11-01 evaluation.tex
edits

In this section, we evaluate \name programs and report the contract profile as
well as illustrating the performance benefits of fine-grained consistency
classification on operations and transactions. We also report on the impact of
the summarization. We implemented the following applications, which includes
RDTs as well as larger applications composed of severals RDTs:

@@

>>>>

In this section, we evaluate \name programs and report their contract profile
as well as illustrating the performance benefits of fine-grained consistency
classification on operations and transactions. We also report on the impact of
the summarization. We implemented the following applications, which includes
RDTs as well as larger applications composed of severals RDTs:

@@

\subsection{Performance}

In this section, we study the performance benefit of fine-grained contract
classification, and the impact of summarization optimization.

\subsection{Configuration}

We deploy \name applications in \emph{clusters} where each cluster is composed
of 5 fully replicated Cassandra replicas within the same datacenter. We
instantiate one shim layer node for every cassandra replica, an place it on the
same VM as the cassandra replica. The clients are instantiated on the same data
center as the store.

### 2014-11-01 implementation.tex
implementation
edits

Replicated data type implementation and the stronger consistency semantics are
enforced in the \emph{shim layer}. Our implementation supports eventual, causal
and strong consistency for operations, and RC, MAV and RR transaction
semantics. All of this functionality is implemented on top of the standard
interface exposed by Cassandra, and illustrates the portability of \name
programming model. Complex business logic is implemented with the help of
transactions on the web-server side, with clients interacting with the
web-service over REST interface. From an engineering perspective, resorting to
an off-the-shelf backing store meant that our entire implementation comprised of
only around 2500 lines of Haskell code, which is packaged as a Haskell
library\footnote{url to the hackage}.

\subsection{Shim Layer}

@@

>>>>

Replicated data type implementation and the stronger consistency semantics are
enforced in the \emph{shim layer}. Our implementation supports eventual, causal
and strong consistency for operations, and RC, MAV and RR transaction
semantics. Complex business logic is implemented with the help of transactions
on the server side, with clients interacting with the web-service over REST
interface. From an engineering perspective, resorting to an off-the-shelf
backing store meant that our entire implementation comprised of only around
2500 lines of Haskell code, which is packaged as a Haskell library\footnote{url
to the hackage}.

% All of this functionality is implemented on top of the standard interface
% exposed by Cassandra, and illustrates the portability of \name programming
% model.
\subsection{Shim Layer}

@@

\KC{Perhaps the following two subsections can be elided/shortened?}
